Bandit Multiclass Classification

### 2018-10-12 ptf_margin.tex
some remarks

\section{Learning intersection of halfspaces with a margin}
Suppose we are given examples $S = \cbr{(x, y)}$, where $x$ is in $\cbr{x \in \fR^d: \| x \| \leq 1}$, and $y$ is in $\cbr{-1,+1}$.
\begin{definition}
Dataset $S$ is said to be separable by an intersection of halfspaces with margin parameter $\gamma > 0$, if there exists $t$ linear classifiers $v_1, \ldots, v_t$ (all of which are in $\cbr{v \in \fR^d: \| v \| \leq 1}$),
such that for every $(x,y)$ in $S$:
\begin{enumerate}
  \item If $y = +1$, then $v_i \cdot x \geq \gamma$ holds simultaneously for all $i$ in $[t]$.
  \item If $y = -1$, then there exists an $i$ in $[t]$, $v_i \cdot x \leq -\gamma$.
\end{enumerate}
\label{def:int-margin}
\end{definition}

@@

\begin{fact}
$S_n^k(\cdot)$ has the following properties:
\begin{enumerate}
\item If $x$ is in $[1, 2^n]$, then $S_n^k(x)$ is in $[1, 1 + \frac 1 k]$. \label{item:sign-rt}
\item If $x$ is in $[-2^{-n}, -1]$, then $S_n^k(x)$ is in $[-1 - \frac 1 k, -1]$. \label{item:sign-lt}
\item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$. \label{item:sign-denom}
\end{enumerate}
\label{fact:newman}
\end{fact}
\begin{proof}
We prove all the items accordingly.
\begin{enumerate}
\item Observe that $S_n^k(x)$ can be written as:
\[ S_n^k(x) = \frac{1 + (-\frac{P_n(x)}{P_n(-x)})^{h(k)}}{ 1 - (-\frac{P_n(x)}{P_n(-x)})^{h(k)} }.  \]
Denote by $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)}$. By item~\ref{item:x-large} of Fact~\ref{fact:pn}, $r \in [0, \frac{1}{2k+1}]$. This implies that
$S_n^k(x) = \frac{1+r}{1-r} \in [1, 1 + \frac 1 k]$.

@@

For the second item, given that $x \geq 1$, $1+x \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \geq 4. \]

\end{proof}

>>>>

\section{Learning intersection of halfspaces with a margin}
Suppose we are given examples $S = \cbr{(x, y)}$, where $x$ is in $\cbr{x \in \fR^d: \| x \| \leq 1}$, and $y$ is in $\cbr{-1,+1}$.
\begin{definition}
Dataset $S$ is said to be separable by an intersection of halfspaces with margin parameter $\gamma > 0$, if there exists $t$ linear classifiers $v_1, \ldots, v_t$ (all of which are in $\cbr{v \in \fR^d: \| v \| \leq 1}$),
such that for every $(x,y)$ in $S$:
\begin{enumerate}
  \item If $y = +1$, then $v_i \cdot x \geq \gamma$ holds simultaneously for all $i$ in $[t]$.
  \item If $y = -1$, then there exists an $i$ in $[t]$, $v_i \cdot x \leq -\gamma$.
\end{enumerate}
\label{def:int-margin}
\end{definition}
\cz{Looking at~\cite{klivans2004learning} and its proof, it assumes that for all $(x,y)$ in $S$, $|v_i \cdot x| \geq \gamma$. In our subsequent proofs, we show that it can be in fact weakened to the condition above, which is also more suitable for online bandit multiclass linear classification.}

@@

\begin{fact}
$S_n^k(\cdot)$ has the following properties:
\begin{enumerate}
\item If $x$ is in $[1, 2^n]$, then $S_n^k(x)$ is in $[1, 1 + \frac 1 k]$. \label{item:sign-rt}
\item If $x$ is in $[-2^{-n}, -1]$, then $S_n^k(x)$ is in $[-1 - \frac 1 k, -1]$. \label{item:sign-lt}
\item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
\cz{This fact is based on discussions with Chen-Yu, which we found important but was omitted by~\cite{klivans2004learning}.}
\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$.
\cz{This is a refined lower bound of Lemma 6 of~\cite{klivans2004learning}; we got rid of the weird
requirement that ``the fractional part of $x$ is at least $2^{-n}$''.}
\label{item:sign-denom}
\end{enumerate}
\label{fact:newman}
\end{fact}
\begin{proof}
We prove all the items accordingly.
\begin{enumerate}
\item Observe that $S_n^k(x)$ can be written as:
\[ S_n^k(x) = \frac{1 + (-\frac{P_n(x)}{P_n(-x)})^{h(k)}}{ 1 - (-\frac{P_n(x)}{P_n(-x)})^{h(k)} }.  \]
Denote by $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)}$. By item~\ref{item:x-large} of Fact~\ref{fact:pn}, $r \in [0, \frac{1}{2k+1}]$. This implies that
$S_n^k(x) = \frac{1+r}{1-r} \in [1, 1 + \frac 1 k]$.

@@

For the second item, given that $x \geq 1$, $1+x \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \geq 4. \]
\end{proof}
